Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
add n 3s lemma
oops pushed non-compilable tex

\begin{lem}\label{lem:n-3s-admissible}
\todo{lemma and proof}
\end{lem}

>>>>

\begin{lem}\label{lem:n-3s-admissible}
Let $(\sx', L', \Delta), (\sx, L,\Delta)$ be log stacky curve with log half-canonical divisors $L'$ and $L$ with signatures $(g; e_1, \ldots, e_{r-1}; \delta)$ and $(g; e_1, \ldots, e_r; \delta)$ with all $e_i=3$ and $L=L'+\frac{1}{3}P$ for some point $P$.  Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
\end{lem}
\begin{proof}\todo{proof}

\end{proof}
